Quantifying Spatially Resolved Hydration Thermodynamics Using Grid Inhomogeneous Solvation Theory [Article v\versionnumber]

### 2022-12-20 manuscript/manuscript.tex
Remove some mentions of gistpp, small changes to code sections

We also show examples using the \software{gistpp} program, which can be obtained from \url{https://github.com/KurtzmanLab/Gist-Post-Processing} (code and documentation).

@@

@@

\begin{lstlisting}[style=cpptraj]
	parm solvated.parm7
	trajin md-01.nc
	autoimage !(:WAT) origin
	# optionally remove the "pme" option
	gist griddim 100 100 100 out gist.dat \
	refdens 0.03287 pme
\end{lstlisting}
\subsubsection{Interpreting and visualizing the results}
Running the GIST analysis above, an output data file (gist.dat) containing all calculated quantities for each voxel in the system is produced. 
Additionally as outlined in section \ref{sec:running_GIST}, various quantities are written to OPenDX files for accessible visualisation.

To faciliate an accessible way to interact with your GIST data, we recommend using the gisttools library for python3. Open the GIST output with gisttools:
\begin{lstlisting}[style=python]
	from gisttools.gist import load_gist_file
	import matplotlib.pyplot as plt
	gist = load_gist_file(
	"gist.dat", struct="solute-centered.pdb",  eww_ref=-9.539)
	print(f'n_frames = {gist.n_frames}, rho0 = {gist.rho0}')
\end{lstlisting}
All information from the output file is now accessible through the gist object. 
If the number of frames of the simulation ($n_frames$) and the reference density (rho0) are not provided, they are automatically detected from the GIST data. 
We will discuss a way to similarly detect the reference energy of the solvent-solvent energy Eww in the advanced section.

@@

Information about the grid is stored in the grid property of the gist object, structural data is stored as mdtraj trajectory in the struct property:
\begin{lstlisting}[style=python]
	print(gist.grid)
	print(gist.struct)
\end{lstlisting}
Gisttools also provides minimal OpenDX writing capabilities to visualize the calculated or modified GIST data. For visualization, you'll most likely want to write out the density-normalized GIST quantities ($X_dens$):

\begin{lstlisting}[style=python]
	gist.save_dx('A_dens', fname)
	with open(fname) as f:
		for l in f.readlines(300):
			print(l, end='')
\end{lstlisting}

\subsection{Applying GIST for the Streptavidin-Biotin complex}
In this section we will apply GIST to the full complex and discuss each step of the process in more detail to outline pitfalls. We will afterwards introduce advanced analysis workflows which allow you to modify and better visualize the resulting data.
\subsubsection{System Preparation and Equilibration}
If you want to skip this section, run 
\begin{lstlisting}[style=bash]
make equilibration-targets
\end{lstlisting}
in the code folder. This assumes that you have Python and Amber set up properly and that \software{pmemd.cuda} is in the PATH.

@@

\subsubsection{Visualizing $\dgsolv$}
Next, we want to visualize the 3-dimensional contributions to the free energy of hydration, as well as the entropy and enthalpy contributions.
You can use PyMol\cite{pymol} or VMD\cite{vmd} to visualize the .dx files from GIST\@.
With \software{gistpp}, you can use the file from the convergence check. Additional OpenDX files can be produced using \inlinecode{gistpp -op makedx}.
With \software{gisttools}, you can create one using e.g., \inlinecode{gist.save\_dx("A\_dens", "A\_dens.dx")}.

>>>>

@@

Most of the visualisations and results in this tutorial can also be obtained using the \software{gistpp} program, which is available from \url{https://github.com/KurtzmanLab/Gist-Post-Processing} (code and documentation). \software{Gistpp} can directly manipulate \software{OpenDX} files from the GIST output. 
Its usage and some examples were shown in a previous tutorial on GIST\cite{Ramsey2016}.

@@

\begin{lstlisting}[style=cpptraj]
	parm solvated.parm7
	trajin md-01.nc
	autoimage !(:WAT) origin
	# optionally remove the "pme" option
	gist griddim 100 100 100 out gist.dat \
	refdens 0.03287 pme
\end{lstlisting}
\subsubsection{Working with the GIST results}
Running the GIST analysis above, an output data file (gist.dat) containing all calculated quantities for each voxel in the system is produced. 
Additionally as outlined in section \ref{sec:running_GIST}, various quantities are written to OPenDX files for accessible visualisation.

To faciliate an accessible way to interact with your GIST data, we recommend using the gisttools library for python3. Open the GIST output with gisttools:
\begin{lstlisting}[style=python]
	from gisttools.gist import load_gist_file
	import matplotlib.pyplot as plt
	gist = load_gist_file(
	"gist.dat", struct="solute-centered.pdb",  eww_ref=-9.539)
	print(f'n_frames = {gist.n_frames}')
	print(f'rho0 = {gist.rho0}')
\end{lstlisting}
All information from the output file is now accessible through the gist object. 
If the number of frames of the simulation ($n_frames$) and the reference density (rho0) are not provided, they are automatically detected from the GIST data. 
We will discuss a way to similarly detect the reference energy of the solvent-solvent energy Eww in the advanced section.

@@

Information about the grid is stored in the grid property of the gist object, structural data is stored as mdtraj trajectory in the struct property:
\begin{lstlisting}[style=python]
	print(gist.grid)
	print(gist.struct)
\end{lstlisting}
Gisttools also provides minimal OpenDX writing capabilities to visualize the calculated or modified GIST data. For visualization, you'll most likely want to write out the density-normalized GIST quantities (X\_dens):

\begin{lstlisting}[style=python]
	gist.save_dx('A_dens', ')
	with open(fname) as f:
		print([next(f) for x in range(10)])
\end{lstlisting}

\subsubsection{Visualization the GIST results}
Visualizing the GIST quantities is possible through the OpenDX (.dx) files, either provided directly from the GIST calculation or output by the gisttools library. 
\subsection{Applying GIST for the Streptavidin-Biotin complex}
In this section we will apply GIST to the full complex and discuss each step of the process in more detail to outline pitfalls. We will afterwards introduce advanced analysis workflows which allow you to modify and better visualize the resulting data.
\subsubsection{System Preparation and Equilibration}
If you want to skip this section, run 
\begin{lstlisting}[style=bash]
make equilibration-targets
\end{lstlisting}
in the code folder. This assumes that you have Python and Amber set up properly and that \software{pmemd.cuda} is in the PATH.

@@

\subsubsection{Visualizing $\dgsolv$}
Next, we want to visualize the 3-dimensional contributions to the free energy of hydration, as well as the entropy and enthalpy contributions.
You can use PyMol\cite{pymol} or VMD\cite{vmd} to visualize the .dx files from GIST\@.
%With \software{gistpp}, you can use the file from the convergence check. Additional OpenDX files can be produced using \inlinecode{gistpp -op makedx}.
With \software{gisttools}, you can create one using e.g., \inlinecode{gist.save\_dx("A\_dens", "A\_dens.dx")}.
